\documentclass[9pt, a4paper]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{lmodern}
% \usepackage{helvet}
% \usepackage{sans}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{marvosym}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{framed}
\usepackage{fontawesome}
\pagestyle{empty}
\setlist{nosep}
% \usepackage[default]{sourcesanspro}
% \usepackage[default,regular,bold]{sourceserifpro}
% \renewcommand{\familydefault}{\sfdefault}
\setlength{\parskip}{0.2em}
\renewcommand{\baselinestretch}{1}
\setlength{\parindent}{0em}

\titleformat*{\section}{\centering\bfseries\sffamily\large\color{black}}

% \titleformat{name=\section}
%   {\centering\sffamily\bfseries\Large}
%   {}
%   {0pt}
%   {\colorsection}
\titlespacing*{\section}{0pt}{0.5\baselineskip}{0.25\baselineskip}

\newcommand{\colorsection}[1]{%
  \colorbox{gray!10}{\parbox{\dimexpr\textwidth-2\fboxsep}{#1}}}

\geometry{left=1.5cm, right=1.5cm, top=1cm, bottom=1cm}
% \geometry{top=1cm, bott}

\title{Resume}
\author{Matthew Low}
\date{November 2019}

\begin{document}

% Heading stuff

\begin{center}
\Huge{\sffamily\textbf{\color{black} Matthew Low}}\normalsize

\Letter \ \href{mailto:m.low@uq.net.au}{\nolinkurl{m.low@uq.net.au}} \quad \ComputerMouse \ \href{https://mlow.dev}{\nolinkurl{mlow.dev}} \quad \faGithub \ \href{https://github.com/mattchrlw}{\nolinkurl{github.com/mattchrlw}} \quad \Telefon \ (+61) xxx xxx xxx
\end{center}


% \textit{Hi! I'm a 3rd year mathematics and computer science student at the University of Queensland with experience in a variety of languages and environments as well as strong mathematical and statistical skills. My interests lie in algorithms, machine learning, front-end web development, and design.}

% \rule{\textwidth\color{gray!80}}{0.5pt}
\section*{Education}
% \textbf{The University of Queensland} Bachelors of Mathematics and Computer Science
% \hfill \textit{Feb 2018--Present}\\
% Specialisations in Machine Learning, Data Analytics \& Operations Research, GPA 6.00/7.00

% \textbf{The University of Queensland (UQ)} Bachelors of Mathematics/Science, GPA 6.06/7.00

% \textbf{The University of Queensland (UQ)}, Honours\hfill \textit{Feb 2022--Dec 2022}\\
% Bachelors of Science (Honours) in Computer Science. 

\textbf{The University of Queensland (UQ)}, Undergraduate, GPA 6.25/7.00
\hfill \textit{Feb 2018--Nov 2021}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
\item Bachelors of Mathematics and Science majoring in \textbf{Statistics \& Computer Science}.
% \hfill \textit{Feb 2019--Nov 2021}
% \item Bachelors of Mathematics/Computer Science (incomplete) \hfill \textit{Jul 2018--Nov 2019}
% \item Bachelors of Engineering (Hons)/Computer Science (incomplete) \hfill \textit{Feb 2018--Jul 2018}
\end{itemize}
% (equivalent to US GPA 3.83/4)

% \textbf{St Peters Lutheran College}, High School (Queensland Certificate of Education), OP 3 \hfill \textit{Jan 2013--Nov 2017}

\section*{Experience}

\textbf{Software Developer Intern}, Atlassian \hfill \textit{Nov 2020--Feb 2021}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Worked as a full-stack developer on the \textit{Your Work} team, developing cross-platform notifications \& activity experiences.
    \item Worked with Java/Spring Boot-based backend and React \& TypeScript on the frontend, with Mockito/WireMock
\end{itemize}
% \begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
%     \item ...
% \end{itemize}

\textbf{Casual Research Assistant}, School of Information Technology and Electrical Engineering, UQ \hfill \textit{Jul 2020--Present}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Worked on the \textit{Elpis} project, a tool allowing linguists with minimal computational experience to build their own speech recognition models to automatically transcribe audio.
\end{itemize}

\textbf{Software Developer}, Department of Environment and Science, Queensland Government \hfill \textit{Nov 2019--Present}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Worked as a contractor for a number of projects to clients around the department.
    \item Successfully delivered the \textit{Queensland Herbarium 2019 Census} using a MySQL/MS SQL Server backend, automating the census process for the first time.
    \item Developed full-stack web applications for the visualisation and processing of water quality data.
\end{itemize}

\textbf{Tutor (Teaching Assistant)}, The University of Queensland \hfill \textit{Feb 2020--Present}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Delivered solo tutorial-style classes and collaborative workshops to students undertaking coursework in mathematics, statistics and computer science.
    \item \textit{Semester 2, 2020}: COMP3506 \textit{Algorithms and Data Structures}, STAT1301 \textit{Advanced Analysis of Scientific Data}.
    \item \textit{Semester 1, 2020}: MATH1050 \textit{Mathematical Foundations}.
\end{itemize}

\textbf{Summer Research Scholar}, School of Mathematics and Physics, UQ \hfill \textit{Nov 2019--Feb 2020}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Investigated a variety of numerical optimisation algorithms used in machine learning.
    \item Performed experiments on the runtime of such algorithms on various datasets in MATLAB.
    \item Experimented with various novel modifications on traditional algorithms.
\end{itemize}

\textbf{Robotics Mentor}, St Peters Lutheran College \hfill \textit{May 2019--Nov 2019}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Assisted students from Years 5--12 with programming \& building LEGO Mindstorms EV3 robots.
    \item Performed general duties during robotics sessions.
\end{itemize}

% \textbf{Leadership and Mentoring in Science Program}, Faculty of Science, UQ \hfill \textit{Jun 2019--Nov 2019}
% \begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
%     \item Participated in a number of events and completed workshops centered on leadership in science.
% \end{itemize}

% \textbf{Start-Up China Program}, Dalian Neusoft University of Information \hfill \textit{Jun 2019--Jul 2019}
% \begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
%     \item Prepared a business plan and implemented a mock-up product in 4 weeks for the nutrition industry.
% \end{itemize}

\section*{Skills}
\textbf{Languages}: Python, Java, C++, MATLAB, C, SQL, HTML5, CSS, JavaScript, R, TypeScript, Shell, Julia, \LaTeX

\textbf{Technologies}: Git, React, AWS, Docker, Spring Boot, MySQL, SQL Server, PostgreSQL, Node.js, Jenkins, Vagrant, Gurobi

% \textbf{Applications}: Adobe Photoshop, Adobe Illustrator, Adobe InDesign, Jira, Confluence, Trello

\section*{Projects}

\href{https://github.com/summerprogram2019/orange}{\faGithub} \textbf{Orange (group project, Start-Up China Program)}: A nutrition application for managing daily intakes and scanning \& recognising foods using machine learning, developed with Django and Bootstrap. My focus was on the Bootstrap-based front end of the application.

\href{https://github.com/mattchrlw/yeetbeat}{\faGithub} \textbf{YeetBeat (group project, UQCS Hackathon 2019)}: A music guessing game, delivering snippets of audio to multiple users. Developed with Heroku, Bootstrap and NodeJS. My focus was on the Bootstrap-based front end of the application.

\href{https://github.com/mattchrlw/mimicraft}{\faGithub} \textbf{Mimicraft}: A 3D Minecraft clone built with JavaFX 3D Graphics libraries.

\href{https://github.com/mattchrlw/pyfoil}{\faGithub} \textbf{PyFoil}: A Python script that parses and processes airfoil data for use in aerodynamic analysis, using \texttt{subprocess} to interface with an existing command-line application \texttt{XFOIL}.

\textbf{Eurovision Online}: Developed within the space of a few weeks a serverless Firebase-based web application with a React frontend, processing hundreds of votes for a fan-based \textit{Eurovision Song Contest}.

\section*{Volunteering}
\textbf{Committee Member}, University of Queensland Computing Society \hfill \textit{Sep 2020--Present}

\textbf{Secretary}, University of Queensland Computing Society \hfill \textit{Oct 2019--Sep 2020}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Organised meetings with fellow members of the committee and took minutes.
    \item Handled communication over email and social media channels.
    \item Communicated with companies and secured sponsorships.
\end{itemize}

\textbf{President}, Mathematics Students Society UQ \hfill \textit{Oct 2020--Present}

\textbf{Industry Liaison Officer}, Mathematics Students Society UQ \hfill \textit{Sep 2019--Oct 2020}
\begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
    \item Helped organise and run a number of society events including \textit{Wine and Cheese} and \textit{Lawn Bowls}.
    \item Communicated with potential sponsors for the society and secured a record number of sponsorships.
    \item Designed the majority of the society's materials, including a redesign of our logo and branding.
\end{itemize}

% \textbf{Information Technology Prefect}, St Peters Lutheran College \hfill \textit{Sep 2016--Sep 2017}
% \begin{itemize}[label=\textcolor{gray!80}{\textbullet}]
%     \item Assisted with AV in various events, especially during technical difficulties.
%     \item Set up a student IT helpdesk for common issues such as software installation and email setup.
% \end{itemize}


\section*{Awards}

2020: \textbf{Dean's Commendation for Academic Excellence} (Semester 1 and 2), \textit{The University of Queensland}

2019--2020: \textbf{Summer Research Scholarship}, \textit{The University of Queensland}

2019: \textbf{New Colombo Plan Grant} for the Start-Up China Program, \textit{The University of Queensland}

2019: \textbf{1st Place Newcomers}, UQCS Hackathon 2019, \textit{UQ Computing Society}

2019: \textbf{1st Place}, Industry vs Student Showdown 2019 (HackerRank competition), \textit{QUT Code Network}

% \color{gray}\raggedleft\textit{References available upon request.}

\end{document}
