%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[a4paper, 10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{geometry}

% \usepackage{fontspec}
\usepackage{xhfill}
\usepackage[T1]{fontenc}
\usepackage{framed}

\renewcommand{\baselinestretch}{1}

\geometry{left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm}

% \setmainfont{Helvetica Neue Light}[Scale=1]
% \setmonofont{SF Mono Light}[Scale=0.9]


%\allsectionsfont{\normalfont\sffamily\bfseries}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\sffamily\bfseries{\raggedright}
}{}{0em}{}[\titlerule\vspace{-3pt}]
%\titlerule
%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% \addfontfeature{LetterSpace=1}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge \sffamily Matthew Low} & Email: \href{mailto:m.low@uqconnect.edu.au}{\texttt{m.low@uqconnect.edu.au}}\\
  \href{https://mattchrlw.github.io}{\texttt{https://mattchrlw.github.io}} & Mobile: 0435 930 130 \\ \href{https://www.linkedin.com/in/matthew-c-low}{\texttt{https://www.linkedin.com/in/matthew-c-low}}  \\
\end{tabular*}

\begin{center}
\textit{
2\textsuperscript{nd} year mathematics and computer science student at the University of Queensland with experience in a variety of languages and environments as well as strong mathematical and statistical skills. My interests lie in algorithms, machine learning, operations research, optimisation, front-end web development and graphic design.}
\end{center}
%-----------EDUCATION-----------------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelors of Mathematics and Computer Science}{Brisbane, Australia}
      {The University of Queensland; GPA: 6.00/7.00}{Feb. 2018 -- Dec. 2021}
      \resumeItemListStart
        \resumeItem{Major}
          {Machine Learning}
        \resumeItem{Relevant Coursework}
          {Numerical Linear Algebra \& Optimisation, Operations Research \& Mathematical Planning, Statistical Modelling \& Analysis, Advanced Calculus \& Linear Algebra II, Mathematical Analysis, Probability \& Statistics, Algorithms \& Data Structures, Computer Systems Principles \& Programming}
%        \resumeItem{Future Relevant Coursework (completed by Summer 2019)}{Computer Systems Principles \& Programming, Algorithms \& Data Structures, Statistical Modelling \& Analysis}
      \resumeItemListEnd
    \resumeSubheading
      {High School}{Brisbane, Australia}
      {St Peters Lutheran College; OP: 3}{Jan. 2013 -- Nov. 2017}
      \resumeItemListStart
        \resumeItem{Subjects}
          {Information Technology Systems (Dux), Mathematics B, Physics, Information Processing Technology, Accounting, English}
%        \resumeItem{Dux}
%          {Information Technology Systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
  
    \resumeSubheading
    {Start-Up China Summer Program}{Dalian, P.R. China}{Dalian Neusoft University of Information}{Jun. 2019 -- Jul. 2019}
    \resumeItemListStart
      \resumeItem{IT Innovation and Entrepreneurship Program}{Prototyped and developed a software product for the Chinese market, under the Australian Government's New Colombo Plan scholarship grant for students studying in the Asia-Pacific region. This product was a nutrition application for managing daily intakes and scanning \& recognising foods using machine learning.}
      \resumeItemListEnd


  	\resumeSubheading
  	{Robotics Mentor}{Brisbane, Australia}{St Peters Lutheran College}{May. 2019 -- Present}
  	\resumeItemListStart
  		\resumeItem{Mentoring}{Assisting students from Years 5-12 in the extra-curricular Robotics program at the college with programming and building Lego Mindstorms EV3 robots.}
  		\resumeItemListEnd

    \resumeSubheading
      {Information Technology Prefect}{Brisbane, Australia}
      {St Peters Lutheran College}{Sep. 2016 -- Sep. 2017}
      \resumeItemListStart
        \resumeItem{Events}
          {Assisted with the usage of technology in various events. Acted as an informal assistant if any technical difficulties arose during school events.}
        % \resumeItem{Learning Management System}
        %   {Assisted with the implementation of the new learning management system, Firefly, rolled out during 2017, helping students learn the new system. Produced videos and other instructional material to assist students with the usage of Firefly.}
        \resumeItem{Student IT Helpdesk}
          {Assisted students with issues with their computer, such as software installation and email setup.}
        \resumeItem{Computer Club}
          {Taught some basic computer skills to junior high as well as senior school students such as programming in JavaScript and using Photoshop.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{PROJECTS}
  \resumeSubHeadingListStart
    \resumeSubItem{Orange (group project)}
      {A nutrition application for managing daily intakes and scanning \& recognising foods using machine learning, developed with Django and Bootstrap.}
    \resumeSubItem{YeetBeat (group project)}
      {A music guessing game, synchronously delivering snippets of audio to multiple users developed with Heroku, Bootstrap and NodeJS.}
  	\resumeSubItem{PyFoil}
      {A Python script that parses and processes airfoil data for use in aerodynamic analysis, using subprocess to interface with an existing command-line application XFOIL.}
    \resumeSubItem{measure-theory}
      {A website and associated Python script that parses, calculates and provides song chart breakdowns for the popular dance game In the Groove (similar to Dance Dance Revolution).}
    \resumeSubItem{Blackboard Refresh}
      {A CSS/JavaScript userscript that re-styles and provides enhancements to the existing UQ Blackboard interface.}
    \resumeSubItem{Java 3D Game}
      {A Java third-person 3D block building game based on JavaFX and implemented using object-oriented programming principles.}
    % \resumeSubItem{Skydiving Database}
    %   {A skydiving company relational database application using Microsoft Access and SQL, with initial database design work using the VisioModeler application to design ORM diagrams.}
%    \resumeSubItem{The Hour Glass}
%      {An interactive kiosk application for The Hour Glass company using the Animate CC application, using the HTML5 Canvas framework.}
%    \resumeSubItem{Rhythm Game}
%      {A rhythm game developed using the LOVE2D framework, based on the Lua programming language.}
  \resumeSubHeadingListEnd


\section{OTHER}
  \resumeSubHeadingListStart
    \resumeSubItem{Awards}
        {}
    \resumeItemListStart
      \resumeItem{1st Place Newcomers}{UQCS Hackathon 2019, UQ Computing Society}
      \resumeItem{1st Place}{Industry vs Student Showdown 2019, QUT Code Network}
    \resumeItemListEnd
    \resumeSubItem{Languages}
      {Python, Java, MATLAB, C, JavaScript, SQL, HTML, CSS, \LaTeX, Lua}
    % \resumeSubItem{Learning}
    %   {TypeScript, R, C++, Vue.js}
    \resumeSubItem{Technologies}
      {Git, Bash, Vim, Unix/Linux, Gurobi, PHPMyAdmin, Corona SDK, LÖVE2D, RStudio}
    \resumeSubItem{Applications}
      {Photoshop, Illustrator, Animate, Dreamweaver, Microsoft Office}
    \resumeSubItem{Software engineering skills}
      {Object-oriented programming, database design, unit \& mutation testing}
    \resumeSubItem{Quantitative skills}
      {Linear, integer \& dynamic programming, calculus, lin. alg., discrete maths, statistics}
    \resumeSubItem{Certifications}
      {Adobe Certified Associate in Photoshop, Adobe Certified Associate in Animate}
    \resumeSubItem{Extracurriculars}
      {Member of UQ Computing Society, QUT Code Network \& Mathematics Students Society}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
